Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-04-29 concurrency/CONCUR 2023/paper.tex
fixed breakage

\author{Duc Than Nguyen}{University of Illinois at Chicago, USA \and \url{http://dnguye96.people.uic.edu} }{dnguye96@uic.edu}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional. Use additional curly braces to indicate the correct name splitting when the last name consists of multiple name parts.

\author{Lennart Beringer}{Princeton University, USA \and \url{https://www.cs.princeton.edu/~eberinge} }{eberinge@cs.princeton.edu}{https://orcid.org/0000-0002-1570-3492}{(Optional) author-specific funding acknowledgements}

\author{William Mansky}{University of Illinois at Chicago, USA\and \url{https://mansky.lab.uic.edu/} }{mansky1@uic.edu}{https://orcid.org/0000-0002-5351-895X}{(Optional) author-specific funding acknowledgements}

\author{Shengyi Wang}{Princeton University, USA \and \url{https://www.cs.princeton.edu/~shengyiw} }{shengyiw@cs.princeton.edu}{https://orcid.org/[0000-0002-2286-8703}{(Optional) author-specific funding acknowledgements}

@@

\Copyright{Duc Than Nguyen and William Mansky} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

@@

\keywords{concurrent separation logic, fine-grained locking, logical atomicity,
	Verified Software Toolchain, Iris} %TODO mandatory; please add comma-separated list of keywords

>>>>

\author{Duc Than Nguyen}{University of Illinois at Chicago, USA \and \url{http://dnguye96.people.uic.edu} }{dnguye96@uic.edu}{https://orcid.org/0000-0002-6810-897X}{%(Optional) author-specific funding acknowledgements
}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional. Use additional curly braces to indicate the correct name splitting when the last name consists of multiple name parts.

\author{Lennart Beringer}{Princeton University, USA \and \url{https://www.cs.princeton.edu/~eberinge} }{eberinge@cs.princeton.edu}{https://orcid.org/0000-0002-1570-3492}{}

\author{William Mansky}{University of Illinois at Chicago, USA\and \url{https://mansky.lab.uic.edu/} }{mansky1@uic.edu}{https://orcid.org/0000-0002-5351-895X}{}

\author{Shengyi Wang}{Princeton University, USA \and \url{https://www.cs.princeton.edu/~shengyiw} }{shengyiw@cs.princeton.edu}{https://orcid.org/[0000-0002-2286-8703}{}

@@

\Copyright{Duc Than Nguyen, Lennart Beringer, William Mansky, and Shengyi Wang} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

@@

\keywords{concurrent separation logic, fine-grained locking, logical atomicity, theorem proving,
	Verified Software Toolchain, Iris} %TODO mandatory; please add comma-separated list of keywords
